\documentclass{muratcan_cv}

\setname{Wen Zhang}{}
\setaddress{Montréal, Canada}
\setmobile{+1 514-261-1811}
\setmail{wen.x.zhang@gmail.com}
% \setcitizenship{Eldian Citizen}
\setlinkedinaccount{https://www.linkedin.com/in/wen-zhang-172a8026} 
\setgithubaccount{https://spoony-mushroom.github.io/landing-page/}
\setthemecolor{MidnightBlue}

\begin{document}

%Create header
\headerview
\vspace{1ex} % white space
%
\section{Summary}
\explanationdetail{
    Senior software developer with over 10 years of experience working at the intersection of machine learning, computer graphics, and animation.
}
\bigskip
%
\section{Experience}
    \smallskip
    %
    \datedexperience{Unity Technologies}{July 2021 - Present}
    \explanation{Senior Software Developer}{Montréal, QC}
    \explanationdetail{
    \smallskip
     \coloredbullet\ %inserts a space after the bullet
     As an engineer in the AI research group, I am building tools for the Unity Editor to empower content creation with AI, leveraging proprietary ML models for generating animation clips from text and video.

    \smallskip 
     \coloredbullet\ %
     Led the development of the Cluster Display package, which allows for scaling up content to be rendered across multiple screens/nodes, with a focus on mixed reality film sets.
     
     \smallskip\smallskip
    }
     %
    \datedexperience{wrnch, Inc.}{Mar 2015 - Jul 2021} 
     \explanation{Senior Developer/Architect}{Montréal, QC} 
     \explanationdetail{ 
     \smallskip 
     \coloredbullet\ %
      Led the development of the vision-based gesture tracking subsystem in WEBSLINGERS: A Spider-Man Adventure at Walt Disney Parks (Anaheim and Paris).
     
      \smallskip
      \coloredbullet\ %
      Led the productization of our human pose estimation technology into a markerless motion capture engine (C++, CoreML, TensorRT).
     
      \smallskip
      \coloredbullet\ %
      Designed tech stack for real-time vision-based human motion capture, integrating wrnch's deep learning modules with various front-end applications (Python, C++, Unity, Unreal 4, web/Three.js).

      \smallskip
      \coloredbullet\ %
      Implemented algorithms for image enhancement for heterogeneous platforms (CPU/GPU, mobile/desktop/cloud).
     
      \smallskip
      \coloredbullet\ %
      Developed internal tools for debugging and visualization of image processing modules (Qt/C++)

      \smallskip\smallskip
    }
    \datedexperience{iGotcha Media}{Apr 2014 - Mar 2015}
     \explanation{Application Developer}{Montréal, QC} 
     \explanationdetail{
        \smallskip
        \coloredbullet\
        Maintained and developed digital signage player software (.NET)

        \smallskip
        \coloredbullet\
        Developed modern web frontend for cloud-based content management system (AngularJS, Ruby on Rails).

        \smallskip
        \coloredbullet\
        Designed and implemented web-based content creation interface (HTML, AngularJS, Ruby on Rails).

        \smallskip\smallskip
     }
     \datedexperience{Freelance Software Developer/Technologist}{Sep 2012 - Mar 2015}
    %  \explanation{Application Developer}{Montréal, QC} 
     \explanationdetail{
        \smallskip
        \coloredbullet\
        Developed rendering technique in Unity for rendering and lighting 2D hand-drawn artwork in a 3D isometric environment for indie game prototype from Miscellaneum Studios.

        \smallskip
        \coloredbullet\
        Protoyped procedural content generation and controls concepts combining Leap Motion and Oculus Rift for a VR experience entitled "Biocube" in collaboration with the Nation Film Board and KO\_OP Mode.

        \smallskip
        \coloredbullet\
        Programmed interactive installation utilizing Kinect motion capture, generative visuals with Cinder and C++, and sound with Max/MSP, based on my animated short "Reverie.exe", exhibited for the 8th edition of Hothouse at the Nation Film Board.

        \smallskip\smallskip
     }
     \datedexperience{SANDDE Corporation}{Oct 2010 - Sep 2012}
     \explanation{Software Developer}{Montréal, QC} 
     \explanationdetail{
        \smallskip
        \coloredbullet\
        Contributed to the development and mainentance of the SANDDE stereoscopic animation application (C++/OpenGL/Windows)

        \smallskip
        \coloredbullet\
        Created custom vision-based 6DOF input device using commercial webcam for tracking.

        \smallskip
        \coloredbullet\
        Extended graphics engine to support new artistic brush styles.

        \smallskip\smallskip
     }
     
    %  \smallskip
    \bigskip
      
%
\section{Education} 
    \datedexperience{Master of Applied Science - Systems Design Engineering}{2007 - 2009}
    \explanation{University of Waterloo}{Waterloo, ON} 
    \datedexperience{Bachelor of Applied Science - Systems Design Engineering}{2002 - 2007}
    \explanation{University of Waterloo}{Waterloo, ON}
%
\section{Skills}
\newcommand{\skillone}{\createskill{Programming Languages}{C++ \cpshalf C\# \cpshalf Python }}
%
\newcommand{\skilltwo}{\createskill{Technologies}{ Unity \cpshalf Unreal Engine \cpshalf OpenGL \cpshalf CUDA \cpshalf PyTorch}}
%
\createskills{\skillone, \skilltwo}
\vspace{-3mm} % reduces whitespace!
%
\iffalse
\section{Notable Projects}
     %
    \datedexperience{RandoSite.com}{Mar 2021 - Sep 2021}
    \explanation{Full Stack Developer}{San Francisco, CA} 
    \explanationdetail{
    \smallskip 
    \coloredbullet\ %
     Independently built an open-source web application that performs advanced Monte Carlo calculations for options trading, receiving praise from the trading community for its simplicity and accessibility. 
     
     
     \smallskip
     \coloredbullet\ %
     Front and back-end development using the React and Flask (Python) frameworks, respectively. These services were containerized using Docker Compose to enable scalability in the software architecture.
     
     \smallskip
     \coloredbullet\ %
     Used Python optimization techniques to reduce calculation times for a fast API that can serve thousands of users per second. Load balancing in AWS was incorporated to ensure fault-tolerance and reliability of the application.
     
     \smallskip
     \coloredbullet\ %
     Integrated the Azure Active Directory B2C service for secure user authentication and convenient identity management. 
     
    \smallskip
     }
     %
    \datedexperience{RandoApp Android App}{Jan 2018 - Apr 2018}
    \explanation{Full Stack Developer}{San Francisco, CA} 
    \explanationdetail{
    \smallskip
     \coloredbullet\ %
     Collaborated with a team in building an Android application for monitoring the health status of trees in San Francisco. The app would assist the city in its urban planning and sustainability goals. 
    
    \smallskip 
    \coloredbullet\ %
    Implemented the user authentication system using the Android SDK (Java). Google Maps was integrated into the app to enable geotagging of trees and updating their health status by users.
      
     \smallskip
     \coloredbullet\ %
    Test-driven development of all back-end endpoints using JUnit testing. The back-end was deployed on a Tomcat server.   
     
     \smallskip
     }
     %
     \datedexperience{University Space Design Team}{Sep 2016 - May 2018}
    \explanation{Satellite Control Systems Lead}{San Francisco, CA} 
    \explanationdetail{
    \smallskip
     \coloredbullet\ %
     Led a team of prospective engineers in designing the control system for Rando University's first student-led Cube Satellite (CubeSat) project. The satellite would compete in the USA Satellite Design Competition.
    
    \smallskip 
    \coloredbullet\ %
     Simulated the attitude dynamics and kinematics of a CubeSat in MATLAB to optimize controller gains and to size our actuators for power efficiency.
     
     \smallskip
     \coloredbullet\ %
     Implemented PID and B-dot controllers in Python on a Raspberry Pi for the attitude control of a CubeSat prototype, achieving a desired pointing accuracy of less than 15 degrees for our mission.

     \smallskip
    %  \bigskip
     }
%
\section{Publications}
\indent
\explanationdetail{
\smallskip 
\coloredbullet\ %
 \textbf{John Doe} and FirstName LastName, "Super Awesome Modification for UAV Control Systems," \emph{2020 International Conference on Super Cool Stuff (ICSCS)}, Paris, France.
 }
 \fi
\end{document}
